\textbf{Efficient Implementation Strategies for Block Ciphers on ARMv8}\\ {\footnotesize Bachelorarbeit}

### 2023-04-02 Paper/chapters/appendix.tex
remove implementation.tex, fancyhdr

\chapter{Appendix}

\begin{lstlisting}[language=c, caption={gift\_vec\_sliced.h}]
#ifndef GIFT_VEC_SLICED_H
#define GIFT_VEC_SLICED_H

#include <stdint.h>
#include <arm_neon.h>

#define ROUNDS_GIFT_64 28

// expose for benchmarking
uint8x16_t shl(uint8x16_t v, int n);
uint8x16_t shr(uint8x16_t v, int n);
void gift_64_vec_sliced_swapmove(uint8x16_t *restrict a, uint8x16_t *restrict b,
                                 uint8x16_t m, int n);
void gift_64_vec_sliced_bits_pack(uint8x16x4_t m[restrict 2]);

void gift_64_vec_sliced_subcells(uint8x16x4_t cipher_state[restrict 2]);
void gift_64_vec_sliced_subcells_inv(uint8x16x4_t cipher_state[restrict 2]);
void gift_64_vec_sliced_permute(uint8x16x4_t cipher_state[restrict 2]);
void gift_64_vec_sliced_permute_inv(uint8x16x4_t cipher_state[2]);
void gift_64_vec_sliced_generate_round_keys(uint8x16x4_t round_keys[restrict ROUNDS_GIFT_64][2],
                                            const uint64_t key[restrict 2]);

void gift_64_vec_sliced_init(void);

void gift_64_vec_sliced_encrypt(uint64_t c[restrict 16],
                                const uint64_t m[restrict 16],
                                const uint64_t key[restrict 2]);
void gift_64_vec_sliced_decrypt(uint64_t m[restrict 16],
                                const uint64_t c[restrict 16],
                                const uint64_t key[restrict 2]);

#endif
\end{lstlisting}

\begin{lstlisting}[language=c, caption={gift\_vec\_sliced.c}]
#include "gift_vec_sliced.h"

#include <stddef.h>
#include <stdio.h>
#include <string.h>

static uint64_t perm_u64[16] = {
        0x1410050115110400UL, 0x1410050115110400UL,
        0x0501151104001410UL, 0x0501151104001410UL,
        0x1511040014100501UL, 0x1511040014100501UL,
        0x0400141005011511UL, 0x0400141005011511UL,
        0x1612070317130602UL, 0x1612070317130602UL,
        0x0703171306021612UL, 0x0703171306021612UL,
        0x1713060216120703UL, 0x1713060216120703UL,
        0x0602161207031713UL, 0x0602161207031713UL
};

static uint64_t perm_inv_u64[16] = {
        0x1511050114100400UL, 0x1511050114100400UL,
        0x1713070316120602UL, 0x1713070316120602UL,
        0x1115010510140004UL, 0x1115010510140004UL,
        0x1317030712160206UL, 0x1317030712160206UL,
        0x1317030712160206UL, 0x1317030712160206UL,
        0x1511050114100400UL, 0x1511050114100400UL,
        0x1713070316120602UL, 0x1713070316120602UL,
        0x1115010510140004UL, 0x1115010510140004UL
};

static uint8x16x4_t perm[2];
static uint8x16x4_t perm_inv[2];

static uint8x16_t pack_mask_0;
static uint8x16_t pack_mask_1;
static uint8x16_t pack_mask_2;

static const int round_constant[] = {
        // rounds 0-15
        0x01, 0x03, 0x07, 0x0F, 0x1F, 0x3E, 0x3D, 0x3B,
        0x37, 0x2F, 0x1E, 0x3C, 0x39, 0x33, 0x27, 0x0E,
        // rounds 16-31
        0x1D, 0x3A, 0x35, 0x2B, 0x16, 0x2C, 0x18, 0x30,
        0x21, 0x02, 0x05, 0x0B, 0x17, 0x2E, 0x1C, 0x38,
        // rounds 32-47
        0x31, 0x23, 0x06, 0x0D, 0x1B, 0x36, 0x2D, 0x1A,
        0x34, 0x29, 0x12, 0x24, 0x08, 0x11, 0x22, 0x04
};

uint8x16_t shl(uint8x16_t v, int n)
{
        uint64_t l[2];
        vst1q_u64(l, v);
        l[1] = l[1] << n | (l[0] >> (64 - n));
        l[1] <<= n;
        return vreinterpretq_u8_u64(vld1q_u64(l));
}

uint8x16_t shr(uint8x16_t v, int n)
{
        uint64_t l[2];
        vst1q_u64(l, v);
        l[0] = l[0] >> n | (((l[1] << (64 - n)) >> (64 - n)) << (64 - n));
        l[1] >>= n;
        return vreinterpretq_u8_u64(vld1q_u64(l));
}

void gift_64_vec_sliced_swapmove(uint8x16_t *restrict a, uint8x16_t *restrict b, uint8x16_t m, int n)
{

        uint8x16_t t = vandq_u8(veorq_u8(shr(*a, n), *b), m);
        *b = veorq_u8(*b, t);
        *a = veorq_u8(*a, shl(t, n));
}

void gift_64_vec_sliced_bits_pack(uint8x16x4_t m[restrict 2])
{
        // take care not to shift mask bits out of the register
        gift_64_vec_sliced_swapmove(&m[0].val[0], &m[0].val[1], pack_mask_0, 1);
        gift_64_vec_sliced_swapmove(&m[0].val[2], &m[0].val[3], pack_mask_0, 1);
        gift_64_vec_sliced_swapmove(&m[1].val[0], &m[1].val[1], pack_mask_0, 1);
        gift_64_vec_sliced_swapmove(&m[1].val[2], &m[1].val[3], pack_mask_0, 1);

        gift_64_vec_sliced_swapmove(&m[0].val[0], &m[0].val[2], pack_mask_1, 2);
        gift_64_vec_sliced_swapmove(&m[0].val[1], &m[0].val[3], pack_mask_1, 2);
        gift_64_vec_sliced_swapmove(&m[1].val[0], &m[1].val[2], pack_mask_1, 2);
        gift_64_vec_sliced_swapmove(&m[1].val[1], &m[1].val[3], pack_mask_1, 2);

        // make bytes (a0 b0 c0 d0 a4 b4 c4 d4 -> a0 b0 c0 d0 e0 f0 g0 h0)
        gift_64_vec_sliced_swapmove(&m[0].val[0], &m[1].val[0], pack_mask_2, 4);
        gift_64_vec_sliced_swapmove(&m[0].val[2], &m[1].val[2], pack_mask_2, 4);
        gift_64_vec_sliced_swapmove(&m[0].val[1], &m[1].val[1], pack_mask_2, 4);
        gift_64_vec_sliced_swapmove(&m[0].val[3], &m[1].val[3], pack_mask_2, 4);
}

void gift_64_vec_sliced_subcells(uint8x16x4_t cs[restrict 2])
{
        cs[0].val[1] = veorq_u8(cs[0].val[1], vandq_u8(cs[0].val[0], cs[0].val[2]));
        uint8x16_t t = veorq_u8(cs[0].val[0], vandq_u8(cs[0].val[1], cs[0].val[3]));
        cs[0].val[2] = veorq_u8(cs[0].val[2], vorrq_u8(t, cs[0].val[1]));
        cs[0].val[0] = veorq_u8(cs[0].val[3], cs[0].val[2]);
        cs[0].val[1] = veorq_u8(cs[0].val[1], cs[0].val[0]);
        cs[0].val[0] = vmvnq_u8(cs[0].val[0]);
        cs[0].val[2] = veorq_u8(cs[0].val[2], vandq_u8(t, cs[0].val[1]));
        cs[0].val[3] = t;

        cs[1].val[1] = veorq_u8(cs[1].val[1], vandq_u8(cs[1].val[0], cs[1].val[2]));
        t            = veorq_u8(cs[1].val[0], vandq_u8(cs[1].val[1], cs[1].val[3]));
        cs[1].val[2] = veorq_u8(cs[1].val[2], vorrq_u8(t, cs[1].val[1]));
        cs[1].val[0] = veorq_u8(cs[1].val[3], cs[1].val[2]);
        cs[1].val[1] = veorq_u8(cs[1].val[1], cs[1].val[0]);
        cs[1].val[0] = vmvnq_u8(cs[1].val[0]);
        cs[1].val[2] = veorq_u8(cs[1].val[2], vandq_u8(t, cs[1].val[1]));
        cs[1].val[3] = t;
}

void gift_64_vec_sliced_subcells_inv(uint8x16x4_t cs[restrict 2])
{
        uint8x16_t t = cs[0].val[3];
        cs[0].val[2] = veorq_u8(cs[0].val[2], vandq_u8(t, cs[0].val[1]));
        cs[0].val[0] = vmvnq_u8(cs[0].val[0]);
        cs[0].val[1] = veorq_u8(cs[0].val[1], cs[0].val[0]);
        cs[0].val[3] = veorq_u8(cs[0].val[0], cs[0].val[2]);
        cs[0].val[2] = veorq_u8(cs[0].val[2], vorrq_u8(t, cs[0].val[1]));
        cs[0].val[0] = veorq_u8(t, vandq_u8(cs[0].val[1], cs[0].val[3]));
        cs[0].val[1] = veorq_u8(cs[0].val[1], vandq_u8(cs[0].val[0], cs[0].val[2]));

        t            = cs[1].val[3];
        cs[1].val[2] = veorq_u8(cs[1].val[2], vandq_u8(t, cs[1].val[1]));
        cs[1].val[0] = vmvnq_u8(cs[1].val[0]);
        cs[1].val[1] = veorq_u8(cs[1].val[1], cs[1].val[0]);
        cs[1].val[3] = veorq_u8(cs[1].val[0], cs[1].val[2]);
        cs[1].val[2] = veorq_u8(cs[1].val[2], vorrq_u8(t, cs[1].val[1]));
        cs[1].val[0] = veorq_u8(t, vandq_u8(cs[1].val[1], cs[1].val[3]));
        cs[1].val[1] = veorq_u8(cs[1].val[1], vandq_u8(cs[1].val[0], cs[1].val[2]));
}

void gift_64_vec_sliced_permute(uint8x16x4_t cs[restrict 2])
{
        uint8x16x2_t pairs[4] = {
                { .val = { cs[0].val[0], cs[1].val[0] }},
                { .val = { cs[0].val[1], cs[1].val[1] }},
                { .val = { cs[0].val[2], cs[1].val[2] }},
                { .val = { cs[0].val[3], cs[1].val[3] }},
        };

        cs[0].val[0] = vqtbl2q_u8(pairs[0], perm[0].val[0]);
        cs[0].val[1] = vqtbl2q_u8(pairs[1], perm[0].val[1]);
        cs[0].val[2] = vqtbl2q_u8(pairs[2], perm[0].val[2]);
        cs[0].val[3] = vqtbl2q_u8(pairs[3], perm[0].val[3]);

        cs[1].val[0] = vqtbl2q_u8(pairs[0], perm[1].val[0]);
        cs[1].val[1] = vqtbl2q_u8(pairs[1], perm[1].val[1]);
        cs[1].val[2] = vqtbl2q_u8(pairs[2], perm[1].val[2]);
        cs[1].val[3] = vqtbl2q_u8(pairs[3], perm[1].val[3]);
}

void gift_64_vec_sliced_permute_inv(uint8x16x4_t cs[restrict 2])
{
        uint8x16x2_t pairs[4] = {
                { .val = { cs[0].val[0], cs[1].val[0] }},
                { .val = { cs[0].val[1], cs[1].val[1] }},
                { .val = { cs[0].val[2], cs[1].val[2] }},
                { .val = { cs[0].val[3], cs[1].val[3] }},
        };

        cs[0].val[0] = vqtbl2q_u8(pairs[0], perm_inv[0].val[0]);
        cs[0].val[1] = vqtbl2q_u8(pairs[1], perm_inv[0].val[1]);
        cs[0].val[2] = vqtbl2q_u8(pairs[2], perm_inv[0].val[2]);
        cs[0].val[3] = vqtbl2q_u8(pairs[3], perm_inv[0].val[3]);

        cs[1].val[0] = vqtbl2q_u8(pairs[0], perm_inv[1].val[0]);
        cs[1].val[1] = vqtbl2q_u8(pairs[1], perm_inv[1].val[1]);
        cs[1].val[2] = vqtbl2q_u8(pairs[2], perm_inv[1].val[2]);
        cs[1].val[3] = vqtbl2q_u8(pairs[3], perm_inv[1].val[3]);
}

void gift_64_vec_sliced_generate_round_keys(uint8x16x4_t round_keys[restrict ROUNDS_GIFT_64][2],
                                            const uint64_t key[restrict 2])
{
        // TODO shift-and-or

        uint64_t key_state[] = {key[0], key[1]};
        for (int round = 0; round < ROUNDS_GIFT_64; round++) {
                int v = (key_state[0] >> 0 ) & 0xffff;
                int u = (key_state[0] >> 16) & 0xffff;

                // add round key (RK=U||V)
                uint64_t round_key[8] = { 0x0UL };
                for (size_t i = 0; i < 8; i++) {
                        int key_bit_v   = (v >> (2 * i + 0)) & 0x1;
                        int key_bit_u   = (u >> (2 * i + 0)) & 0x1;
                        round_key[0] ^= (uint64_t)key_bit_v << (i * 8);
                        round_key[1] ^= (uint64_t)key_bit_u << (i * 8);

                        key_bit_v   = (v >> (2 * i + 1)) & 0x1;
                        key_bit_u   = (u >> (2 * i + 1)) & 0x1;
                        round_key[4] ^= (uint64_t)key_bit_v << (i * 8);
                        round_key[5] ^= (uint64_t)key_bit_u << (i * 8);
                }

                // add single bit
                round_key[7] ^= 1UL << (7 * 8);

                // add round constants
                round_key[3] ^= ((round_constant[round] >> 0) & 0x1) << (0 * 8);
                round_key[7] ^= ((round_constant[round] >> 1) & 0x1) << (0 * 8);
                round_key[3] ^= ((round_constant[round] >> 2) & 0x1) << (1 * 8);
                round_key[7] ^= ((round_constant[round] >> 3) & 0x1) << (1 * 8);
                round_key[3] ^= ((round_constant[round] >> 4) & 0x1) << (2 * 8);
                round_key[7] ^= ((round_constant[round] >> 5) & 0x1) << (2 * 8);

                // extend bits to bytes
                for (size_t i = 0; i < 8; i++) {
                        round_key[i] |= round_key[i] << 1;
                        round_key[i] |= round_key[i] << 2;
                        round_key[i] |= round_key[i] << 4;
                }

                // load into vector registers (upper and lower part are same)
                round_keys[round][0].val[0] = vdupq_n_u64(round_key[0]);
                round_keys[round][0].val[1] = vdupq_n_u64(round_key[1]);
                round_keys[round][0].val[2] = vdupq_n_u64(round_key[2]);
                round_keys[round][0].val[3] = vdupq_n_u64(round_key[3]);
                round_keys[round][1].val[0] = vdupq_n_u64(round_key[4]);
                round_keys[round][1].val[1] = vdupq_n_u64(round_key[5]);
                round_keys[round][1].val[2] = vdupq_n_u64(round_key[6]);
                round_keys[round][1].val[3] = vdupq_n_u64(round_key[7]);

                // update key state
                int k0 = (key_state[0] >> 0 ) & 0xffffUL;
                int k1 = (key_state[0] >> 16) & 0xffffUL;
                k0 = (k0 >> 12) | ((k0 & 0xfff) << 4);
                k1 = (k1 >> 2 ) | ((k1 & 0x3  ) << 14);
                key_state[0] >>= 32;
                key_state[0] |= (key_state[1] & 0xffffffffUL) << 32;
                key_state[1] >>= 32;
                key_state[1] |= ((uint64_t)k0 << 32) | ((uint64_t)k1 << 48);
        }
}

void gift_64_vec_sliced_init(void)
{
        // permutations
        perm[0] = vld1q_u8_x4((uint8_t*)&perm_u64[0]);
        perm[1] = vld1q_u8_x4((uint8_t*)&perm_u64[8]);

        // inverse permutations
        perm_inv[0] = vld1q_u8_x4((uint8_t*)&perm_inv_u64[0]);
        perm_inv[1] = vld1q_u8_x4((uint8_t*)&perm_inv_u64[8]);

        // packing masks
        pack_mask_0 = vdupq_n_u8(0x55);
        pack_mask_1 = vdupq_n_u8(0x33);
        pack_mask_2 = vdupq_n_u8(0x0f);
}

void gift_64_vec_sliced_encrypt(uint64_t c[restrict 16],
                                const uint64_t m[restrict 16],
                                const uint64_t key[restrict 2])
{
        uint8x16x4_t s[2];
        s[0] = vld1q_u8_x4((uint8_t*)&m[0]);
        s[1] = vld1q_u8_x4((uint8_t*)&m[8]);
        gift_64_vec_sliced_bits_pack(s);

        uint8x16x4_t round_keys[ROUNDS_GIFT_64][2];
        gift_64_vec_sliced_generate_round_keys(round_keys, key);

        for (int round = 0; round < ROUNDS_GIFT_64; round++) {
                gift_64_vec_sliced_subcells(s);
                gift_64_vec_sliced_permute(s);

                s[0].val[0] = veorq_u8(s[0].val[0], round_keys[round][0].val[0]);
                s[0].val[1] = veorq_u8(s[0].val[1], round_keys[round][0].val[1]);
                s[0].val[2] = veorq_u8(s[0].val[2], round_keys[round][0].val[2]);
                s[0].val[3] = veorq_u8(s[0].val[3], round_keys[round][0].val[3]);
                s[1].val[0] = veorq_u8(s[1].val[0], round_keys[round][1].val[0]);
                s[1].val[1] = veorq_u8(s[1].val[1], round_keys[round][1].val[1]);
                s[1].val[2] = veorq_u8(s[1].val[2], round_keys[round][1].val[2]);
                s[1].val[3] = veorq_u8(s[1].val[3], round_keys[round][1].val[3]);
        }

        gift_64_vec_sliced_bits_pack(s);
        vst1q_u8_x4((uint8_t*)&c[0], s[0]);
        vst1q_u8_x4((uint8_t*)&c[8], s[1]);
}

void gift_64_vec_sliced_decrypt(uint64_t m[restrict 16],
                                const uint64_t c[restrict 16],
                                const uint64_t key[restrict 2])
{
        uint8x16x4_t s[2];
        s[0] = vld1q_u8_x4((uint8_t*)&c[0]);
        s[1] = vld1q_u8_x4((uint8_t*)&c[8]);
        gift_64_vec_sliced_bits_pack(s);

        uint8x16x4_t round_keys[ROUNDS_GIFT_64][2];
        gift_64_vec_sliced_generate_round_keys(round_keys, key);

        for (int round = ROUNDS_GIFT_64 - 1; round >= 0; round--) {
                s[0].val[0] = veorq_u8(s[0].val[0], round_keys[round][0].val[0]);
                s[0].val[1] = veorq_u8(s[0].val[1], round_keys[round][0].val[1]);
                s[0].val[2] = veorq_u8(s[0].val[2], round_keys[round][0].val[2]);
                s[0].val[3] = veorq_u8(s[0].val[3], round_keys[round][0].val[3]);
                s[1].val[0] = veorq_u8(s[1].val[0], round_keys[round][1].val[0]);
                s[1].val[1] = veorq_u8(s[1].val[1], round_keys[round][1].val[1]);
                s[1].val[2] = veorq_u8(s[1].val[2], round_keys[round][1].val[2]);
                s[1].val[3] = veorq_u8(s[1].val[3], round_keys[round][1].val[3]);

                gift_64_vec_sliced_permute_inv(s);
                gift_64_vec_sliced_subcells_inv(s);
        }

        gift_64_vec_sliced_bits_pack(s);
        vst1q_u8_x4((uint8_t*)&m[0], s[0]);
        vst1q_u8_x4((uint8_t*)&m[8], s[1]);
}
\end{lstlisting}

>>>>

\appendix
\chapter{C implementations}
\label{app:cimpl}

\section{Implementations for SPN}
\subsection{Table-based}

\lstinputlisting[language=c, caption={\texttt{gift\_table.h}}]{../impl/table/gift_table.h}
\lstinputlisting[language=c, caption={\texttt{gift\_table.c}}]{../impl/table/gift_table.c}

\subsection{Using \texttt{vperm}}

\lstinputlisting[language=c, caption={\texttt{gift\_vec\_sbox.h}}]{../impl/vector/gift_vec_sbox.h}
\lstinputlisting[language=c, caption={\texttt{gift\_vec\_sbox.c}}]{../impl/vector/gift_vec_sbox.c}

\subsection{Bitslicing}

\lstinputlisting[language=c, caption={\texttt{gift\_vec\_sliced.h}}]{../impl/vector/gift_vec_sliced.h}
\lstinputlisting[language=c, caption={\texttt{gift\_vec\_sliced.c}}]{../impl/vector/gift_vec_sliced.c}

\chapter{Lorem dolor}

### 2023-04-02 Paper/chapters/implementation-strategies.tex
remove implementation.tex, fancyhdr

\begin{enumerate}
    \item A register with lookup values
    \item Two or more registers containing data
\end{enumerate}

@@

We can now create permutation tables using the specification of the individual
slice permutations $P_i$ which are then applied to $V_i$ and $V_{i+4}$:

@@

>>>>

\begin{enumerate}
    \item A register with lookup values
    \item One or more registers containing data
\end{enumerate}

@@

We can now create permutation tables using the specification of the individual
slice permutations $P_i$ which are then applied to $V_i$ and $V_{i+4}$
respectively:

@@

\section{Implementation}

Implementations in the C programming language for the presented strategies can
be found in Appendix \ref{app:cimpl}. Although directly writing Assembler code could
result in a small performance benefit, this generally increases the work
necessary by an order of magnitude for only limited results. Instruction-level
optimization and in particular register allocation is left to the compiler.

\subsection{NEON intrinsics}

The header file \texttt{<arm\_neon.h>} provides ARM-specific data and function
definitions including vector data types and C functions for working with these
vectors. These functions are known as NEON intrinsics \cite{neonintr:2022} and
give the programmer a high-level interface to most NEON instructions. Major
advantages of this approach include the ease of development as the compiler
takes over register allocation and load/store operations as well as performance
benefits through compiler optimizations.

Standard vector data types have the format \texttt{uintnxm\_t} with lane width
$n$ in bits and and lane count $m$. Array types of the format
\texttt{uintnxmxc\_t}, $c\in\{2,3,4\}$ are also defined which are used in
operations requiring multiple parameters like \texttt{TBL} or pairwise
load/stores. Intrinsics include the operation name and lane data format as well
as an optional \texttt{q} suffix to indicate operation on a 128-bit register.
Multiplying eight pairs of 16-bit numbers \texttt{a,b} for example can be done
via the following:

\begin{center}
    \texttt{uint16x8\_t result = vmulq\_u16(a, b);}
\end{center}

In this case, the compiler allocates vector registers for \texttt{a},
\texttt{b} and \texttt{result} and assembles the intrinsic to \texttt{MUL
Vr.8H, Va.8H, Vb.8H}. Necessary loads and stores for the result and parameters
are also handled automatically. Of special interest to us are the following
intrinsics, each existing in different variants with different lane widths and
also array types: \\

\begin{table}[h!]
    \centering
    \footnotesize
    \begin{tabularx}{\textwidth}{ll|X}
        Intrinsic && Description \\
        \hline
        \texttt{uint8x16\_t} & \texttt{vreinterpretq\_u8\_u64(uint64x2\_t)} & Explicit casting \\
        \hline
        \texttt{uint64\_t} & \texttt{vgetq\_lane\_u64(void)} & Extract a single lane \\
        \hline
        \texttt{void} & \texttt{vsetq\_lane\_u64(uint64\_t)} & Insert a single lane \\
        \hline
        \texttt{uint64x2\_t} & \texttt{vdupq\_n\_u64(uint64\_t)} & Initialize all lanes to same value \\
        \hline
        \texttt{void} & \texttt{vst1q\_u64(uint64\_t*, uint64x2\_t)} & Store from register to memory \\
        \hline
        \texttt{uint64x2\_t} & \texttt{vld1q\_u64(uint64\_t*, uint64x2\_t)} & Load from memory to register \\
        \hline
        \texttt{uint8x16\_t} & \texttt{veorq\_u8(uint8x16\_t, uint8x16\_t)} & bitwise XOR \\
        \hline
        \texttt{uint8x16\_t} & \texttt{vandq\_u8(uint8x16\_t, uint8x16\_t)} & bitwise AND \\
        \hline
        \texttt{uint8x16\_t} & \texttt{vorrq\_u8(uint8x16\_t, uint8x16\_t)} & bitwise OR \\
        \hline
        \texttt{uint8x16\_t} & \texttt{vmvnq\_u8(uint8x16\_t)} & bitwise NOT \\
        \hline
        \texttt{uint8x16\_t} & \texttt{vqtbl2q\_u8(uint8x16\_t, uint8x16\_t)} & permutation (\texttt{TBL}) \\
    \end{tabularx}
\end{table}
